---
title: "Community Detection"
output: html_notebook
---

Import the graph library and read the graph into igraph
```{r}
library('igraph')
library('igraphdata')
library(networkD3)
library(c2c)
```

Load the GraphML file as an IGRAPH
```{r}
G = read.graph('StrangerThings.graphml', format='graphml')
cat('Number of nodes in graph: ', length(V(G)),'\n')
cat('Number of edges in graph: ', length(E(G)))
```

Remove the self-loops in the network
```{r}
G = simplify(G, remove.loops = TRUE, remove.multiple = FALSE)
cat('Number of nodes in graph: ', length(V(G)),'\n')
cat('Number of edges in graph: ', length(E(G)))
```

Remove the nodes which do not have edges in the network
```{r}
Isolated = which(degree(G)==0)
G2 = delete.vertices(G, Isolated)
cat('Number of nodes in graph: ', length(V(G2)),'\n')
cat('Number of edges in graph: ', length(E(G2)))
```

Plot the graph
```{r}
V(G2)$degree = degree(G2, normalized = FALSE)
L = layout_with_fr(G2)
plot(G2, layout=layout.fruchterman.reingold, rescale=T, edge.arrow.size=.1, vertex.color="red", vertex.label.color=NA, vertex.label.dist=NA, asp = 0, vertex.size = 2, vertex.label.cex = 0.8)
```

Apply Girvan-Newman Algorithm

 1) Convert the directed graph to undirected graph
```{r}
G2.sym = as.undirected(G2, mode= "collapse", edge.attr.comb=list(weight="sum", "ignore"))
```

 2) Compute the edge betweenness for each edge in network
 3) Remove the edge with the highest betweenness.
 4) Recalculate the edge betweennessfor all edges effected by the removal
 5) Repeat from step 2 until no edges remain
```{r}
comm <- cluster_edge_betweenness(G2.sym, weights=NULL, directed=T) 
cat('Number of identified communities: ', length(comm))
```

Plot the dendrogram 
```{r}
dendPlot(comm, mode="hclust", ann=F, xlab=F, ylab=F)
```

Plot the network by grouping the grouping the nodes into their respective communities
```{r}
plot(comm, G2, layout=layout.fruchterman.reingold, rescale=T, edge.arrow.size=.1, vertex.label.color=NA, vertex.label.dist=NA, asp = -20, vertex.size = 2, vertex.label.cex = 0.8) 
```





```{r}
members = membership(comm)
G2.d3 = igraph_to_networkD3(G2, group = members)
# Create force directed network plot
forceNetwork(Links = G2.d3$links, Nodes = G2.d3$nodes, Source = 'source', Target = 'target', NodeID = 'name', Group = 'group',linkColour = "#afafaf", fontSize=12, zoom=T, legend=T,Nodesize=1, opacity = 0.8, charge=-300, width = 1000, height = 1000)
```
Evaluation metrics using Zachary's Karate Club:


1) Define functions

```{r}
#### FUNCTIONS ###################

GirvanNewman <- function(G) {
  #G = as.undirected(G2, mode= "collapse", edge.attr.comb=list(weight="sum", "ignore"))
  community <- cluster_fast_greedy(G, weights=NULL)
  cat('Number of identified communities: ', length(community))
  return (community)
}

Walktrap <- function(G) {
  community <- walktrap.community(G, weights = NULL, steps = 4, merges = TRUE, modularity = TRUE, membership = TRUE )
  cat('Number of identified communities: ', length(community))
  return (community)
}

LeadingEigen <- function(G) {
  community <- leading.eigenvector.community(G, weights = NULL, steps = vcount(G))
  cat('Number of identified communities: ', length(community))
  return (community)
}

Infomap <- function(G) {
  community <- cluster_infomap(G, e.weights = NULL, v.weights = NULL,
  modularity = TRUE )
  cat('Number of identified communities: ', length(community))
  return (community)
}

plotGraph <- function(G, community, num_clusters) {
  community.groups <- cutat(community, num_clusters)
  #community.subtree <- cutree()
dendPlot(community, mode="hclust", ann=F, xlab=F, ylab=F)
  plot(structure(list(membership=community.groups), class="communities"), G, rescale=T, edge.arrow.size=0.1, vertex.label.dist=0, asp =0, vertex.size = 12, vertex.label.cex = 0.8)
}

dynamicGraph <- function(G, community){
  members <- membership(comm)
  G.d3 <- igraph_to_networkD3(G2, group = members)
# Create force directed network plot
forceNetwork(Links = G.d3$links, Nodes = G.d3$nodes, Source = 'source', Target = 'target', NodeID = 'name', Group = 'group',linkColour = "#afafaf", fontSize=12, zoom=T, legend=T,Nodesize=1, opacity = 0.8, charge=-300, width = 1000, height = 1000)
}
```

```{r}
##### EVAlUATION METRICS #######

evaluate_graph <- function(G, V_attr, community, num_comm){
  confusion_matrix <- table(cutat(community, num_comm), vertex_attr(G, V_attr))
  print(confusion_matrix)
  accuracy <- sum(diag(confusion_matrix))/sum(confusion_matrix)
  cat('Accuracy : ', accuracy)
  modularity <- igraph::modularity(community, membership=cutat(community, num_clusters))
  
  cat('Modularity ', modularity)
}
  
##################################
```

2) Plot the Zachary Karate Club

```{r}
#karate = make_graph('Zachary')
data(karate)
summary(karate)
par(mar=c(0,0,0,0))
plot(karate, rescale=T, edge.arrow.size=0.1, vertex.label.dist=0, asp =0, vertex.size = 12, vertex.label.cex = 0.8)
```

3) Apply CD algorithms to Zachary Karate Club and plot dendrograms and community structure

```{r}
Num_clusters <- 2
comm_karate = GirvanNewman(karate)
comm_walk_karate = Walktrap(karate)
comm_eigen_karate = LeadingEigen(karate)
comm_infomap_karate = Infomap(karate)
par(mfrow=c(1,1))
plotGraph(karate, comm_karate, Num_clusters)
plotGraph(karate, comm_walk_karate, Num_clusters)
plotGraph(karate, comm_eigen_karate, Num_clusters)
#plotGraph(karate, comm_infomap_karate, Num_clusters)
plot(comm_infomap_karate, karate, rescale=T, edge.arrow.size=0.1, vertex.label.dist=0, asp =0, vertex.size = 12, vertex.label.cex = 0.8)
```

Plot the dynamic visualization

```{r}
dynamicGraph(G, comm_karate)
```

Get the Confusion Matrix for GirvanNewman
Cited Papers:
http://www.arxiv.org/abs/cond-mat/0408187

```{r}
evaluate_graph(karate, community = comm_karate, V_attr = 'Faction', num_comm = Num_clusters)
```

Get the Confusion Matrix for RandomWalk (WalkTrap)
Cited papers:
http://arxiv.org/abs/physics/0512106

```{r}
evaluate_graph(karate, community = comm_walk_karate, V_attr = 'Faction', num_comm = Num_clusters)
```

Get the Confusion Matrix for Leading Eigenvector of modularity matrix 
cited paper:
htpp://arXiv:physics/0605087

```{r}
evaluate_graph(karate, community = comm_eigen_karate, V_attr = 'Faction', num_comm = Num_clusters)
```

Get the Confusion Matrix for Infomap:
cited papers: http://dx.doi.org/10.1073/pnas.0706851105, http://arxiv.org/abs/0707.0609

```{r}
evaluate_graph(karate, community = comm_infomap_karate, V_attr = 'Faction', num_comm = Num_clusters)
```

```{r}
dolphin = read.graph(file="http://users.dimi.uniud.it/~massimo.franceschet/teaching/datascience/network/R/dolphin.gml", format="gml")

summary(dolphin)
vcount(dolphin)
ecount(dolphin)
V(g)
coords = layout.fruchterman.reingold(dolphin)
plot(dolphin, layout=coords, rescale=T, edge.arrow.size=0.1, vertex.label.dist=0, asp =0.5, vertex.size = 12, vertex.label.cex = 0.2)
```

```{r}
male = V(dolphin)$sex == "M"
female = V(dolphin)$sex == "F"
V(dolphin)$color = "white"
V(dolphin)[male]$color = "blue"
V(dolphin)[female]$color = "pink"
plot(dolphin, layout=coords, vertex.label=NA, rescale=T, edge.arrow.size=0.1, vertex.label.dist=0, asp =0.5, vertex.size = 5, vertex.label.cex = 0.2)
```

```{r}
Num_clusters <- 2
comm_karate = GirvanNewman(karate)
comm_walk_karate = Walktrap(karate)
comm_eigen_karate = LeadingEigen(karate)
comm_infomap_karate = Infomap(karate)
par(mfrow=c(1,1))
plotGraph(karate, comm_karate, Num_clusters)
plotGraph(karate, comm_walk_karate, Num_clusters)
plotGraph(karate, comm_eigen_karate, Num_clusters)
#plotGraph(karate, comm_infomap_karate, Num_clusters)
plot(comm_infomap_karate, karate, rescale=T, edge.arrow.size=0.1, vertex.label.dist=0, asp =0, vertex.size = 12, vertex.label.cex = 0.8)
```

